ST563 Final Project

### 2021-03-11 ST563-FP.Rmd
added description for MLR

# Methods  
## Data Processing & Partitioning 
```{r partition}
# Prepare data for classification
wine$class <- ifelse(wine$quality <= 5, "low", "high") %>% as.factor()

@@

## Multiple Linear Regression

>>>>

# Methods  
## Data Processing
```{r partition}
# Prepare data for classification
wine$class <- ifelse(wine$quality <= 5, "low", "high") %>% as.factor()

@@

## Multiple Linear Regression
Multiple Linear Regression is the extension of simple linear regression to a set of multiple predictor variables. The goal of multiple linear regression is to model the linear relationship between a continuous response and two or more predictor variables. Like simple linear regression, coefficient estimates are found by minimizing the sum of the squared errors. The formula for a multiple linear regression model with $p$ predictor variables is as follows:
$$
\begin{aligned}
&Y_i = \beta_0 + \beta_1X_{i1} + \beta_2X_{i2} + ... + \beta_pX_{ip} + \epsilon_i, \\
& \quad \text{where for } i = n \text{ observations}, \\
& \quad y_i = \text{dependent variable (response)} \\
& \quad x_{ji} = \text{indpendent variables } (j = 1, ... , p) \\
& \quad \beta_0 = \text{y-intercept} \\
& \quad \beta_j = \text{slope coefficients for each variable} \\
& \quad \epsilon_i = \text{residuals (error term of model)} \\
\end{aligned}
$$

The multiple linear regression model is subject to the following assumptions about the data:
  * Linear relationship between response and predictors
  * No collinearity between predictor variables
  * $y_i$'s are iid
  * $\epsilon_i \sim N(0, \sigma^2)$

The biggest benefit to using a multiple linear regression model is its interpretability and ease of use. The coefficients can be computed efficiently and they are have clear and easy interpretations. It is also possible to make inference on any of the variables or linear combination of variables. The most signficiant drawback of using the multiple linear regression model is that, like the logistic regression model, it is subject to distributional assumptions, meaning that if the assumptions are violated, our estimates and inference will be unstable at best and invalid at worst.
